Interval Probability and Measurement for Fuzzy Quantum Theories

### 2016-08-21 prob.tex
prob.tex Updating...

\section{Quantum Computing on Quantum Interval-valued Probability Measures}

We give up the idea of representing a quantum state as a density matrix,
and compute the quantum state as a quantum interval-valued probability
measure directly.

@@

>>>>

\yutsung{I think there are two possible approaches to complete the
story.

Our original plan was to put the Mermin v.s. Meyer debate here, and
move on to the discrete quantum probability measure. Then, discrete
real-valued quantum probability measures are expected to fail because
of John's proof, and we hope discrete interval-valued Gleason's theorem
can work in some sense? This story might go to section~\ref{sec:DQT}.
The problem of this approach is that Because we don't really use $\mathbb{C}$
in example~\ref{ex:three-dimensional-three-value}, I could expect
example~\ref{ex:three-dimensional-three-value} is highly likely
to serve as an counterexample for discrete interval-valued Gleason's
theorem...

Another possible approach is to tell everybody: because Gleason's
theorem is an accident, the original way to formulate to a quantum
system as a state vector or density matrix is an accident. If we want
to do thing correct, we should work on quantum (real/interval)-valued
probability measure directly. This approach might go to section~\ref{sec:QC}.
The problem of this approach is that we need an concrete example to
show it is possible to work on quantum (real/interval)-valued probability
measure directly. More precisely, we might need to verify tensor product
and quantum teleportation works in this model...}

\section{\label{sec:DQT}(One possible approach) Discrete Quantum Theory}

\subsection{Discrete Quantum Real-valued Probability Measures}

Killed by John... Need to be typed...

\subsection{Discrete Quantum Interval-valued Probability Measures}

Discrete interval-valued Gleason's theorem should be here, but we
don't know whether it works or not... Might need to put some strange
conditions to by-pass the counterexample corresponding to example~\ref{ex:three-dimensional-three-value}.

\section{\label{sec:QC}(Another possible approach) Quantum Computing on Quantum
(Real/Interval)-valued Probability Measures}

We give up the idea of representing a quantum state as a density matrix,
and compute the quantum state as a quantum (real/interval)-valued
probability measure directly.

@@

\subsection{Tensor Product and Partial Measurement}

\yutsung{Quantum Fubini Theorem?}
